### 2017-07-27 Paper01_EnthalpyAndCrystallization.tex
Images - All but Dynmaic XRD split into single images

%code to put 2 images side by side in a figure
\begin{figure}[b]
	\centering
	%Image 1
	\begin{subfigure}[htbp]{0.495\textwidth}
		\includegraphics[width=\textwidth]{DSC_Fragility_Bulk.png}
		\caption{}
		\label{fig:DSC_vHeatingRate_Bulk}
	\end{subfigure}
	%Image 2
	\begin{subfigure}[htbp]{0.495\textwidth}
		\includegraphics[width=\textwidth]{Bulk_Onset_Peaks_Relaxed_120C.png}
		\caption{}
		\label{fig:DSC_Onsets_Bulk}
	\end{subfigure}
	\caption{(a) Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample. (b) The \Tg s and \Tx es of the bulk \MgZnCa~ at all heating rates. }%global caption
	\label{fig:DSC_Bulk}
\end{figure}

%code to put 2 images side by side in a figure
\begin{figure}[b]
	\centering
	%Image 1
	\begin{subfigure}[htbp]{0.495\textwidth}
		\includegraphics[width=\textwidth]{DSC_Fragility_Film.png}
		\caption{}
		\label{fig:DSC_vHeatingRate_Film}
	\end{subfigure}
	%Image 2
	\begin{subfigure}[htbp]{0.495\textwidth}
		\includegraphics[width=\textwidth]{Onsets_BulkandFilm.png}
		\caption{}
		\label{fig:DSC_Onsets_Film}
	\end{subfigure}
	\caption{(a) Unrelaxed film \MgZnCa~ heated at various heating rates. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample. (b) The \Tg s and \Tx es of the bulk and film \MgZnCa~ at all heating rates. }%global caption
	\label{fig:DSC_Film}
\end{figure}

>>>>

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.55\textwidth]{DSC_Fragility_Bulk.png}
	\caption[Table of contents Capition]{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
	\label{fig:DSC_vHeatingRate_Bulk}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.55\textwidth]{DSC_Fragility_Bulk.png}
	\caption[Table of contents Capition]{Unrelaxed film \MgZnCa~ heated at various heating rates. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
	\label{fig:DSC_vHeatingRate_Film}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.55\textwidth]{Bulk_Onset_Peaks_Relaxed_120C.png}
	\caption[Table of contents Capition]{The \Tg s and \Tx es of the bulk \MgZnCa~ at all heating rates. }%global caption
	\label{fig:DSC_Onsets_Bulk}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.55\textwidth]{Onsets_BulkandFilm.png}
	\caption[Table of contents Capition]{The \Tg s and \Tx es of the bulk and film \MgZnCa~ at all heating rates. }%global caption
	\label{fig:DSC_Onsets_BulkFilm}
\end{figure}
